%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Technical Support Specialist \ Technical Operations} % Job title
{Askia, LLC} % Organization
{Los Angeles, CA} % Location
{Apr. 2015 - Present} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Manage client support queries utilizing Zendesk ticketing system.}
\item {Assist Head of Sales by cultivating intuitive and customized software demonstrations.}
\item {Provide specialized software training for new and prospective clients.}
\item {Assistance in the creation and editorialization of articles to expand on product knowledge for ease of client use.}
\item {Provide remote hosting support through VM Management/Server Monitoring.}
\item {Utilize basic knowledge of web development and programming for numerous client consultation projects.}
\end{cvitems}
}

%------------------------------------------------    

\cventry
{Security Officer} % Job title
{Securitas Security Services} % Organization
{Orlando, FL} % Location
{May. 2011 - Feb, 2013} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Maintained daily shift log and assisted in the prevention of crime in area while maintaining a safe environment.}
\item {Performed mobile foot patrols of perimeters ensuring no trespassing, damage to property or breaking and entering occurred.}
\item {Conducted field interviews and made reports of any and all incidents and reported activities to local law enforcement.}
\end{cvitems}
}

\end{cventries}